\speculake: Hiding Malware in Speculative Execution

### 2018-11-28 paper/payloads.tex
added Nested spec Figure and Key for execution figures.
add reference to new figure and clarify speculative entry point != speculative key

However, this toy example is meant only as an illustrative example of arbitrary
computation, notas a robust means of obfuscation. Indeed, even the initial state
of a Turing machine alone may reveal a significant amount of information.
Furthermore, the analyst may attempt to locate potential speculative entry
points, even without the help of the trigger program. We describe ways to address
both of these next.

@@

To increase security, we instead use nested speculation to \emph{chain} entry points
together. Rather than derive
the key from a single entry point, we have each potential entry point perform
another indirect jump that the CPU cannot immediately resolve, forcing it to
speculate while already executing speculatively. The predicted target of that jump
will also be determined by the trigger program. For example, if the trigger
program makes 30 training jumps, followed by 10 additional indirect jumps, and
the payload program performs the same 30 training jumps before a stall, the CPU
will predict the payload program will also perform the next 10 jumps. If each
jump has the potential to land in up to 1024 possible locations, this would
provide in total $1024^{10} = 2^{100}$ possible keys, or 100~bits of security.
We describe our implementation of nested speculative execution in
Section~\ref{subsec:impl-aes}, where we achieve 128~bits of security.
%Section~\ref{subsec:nested-spec}.

>>>>

However, this toy example is meant only as an illustrative example of arbitrary
computation, not as a robust means of obfuscation. Indeed, even the initial
state of a Turing machine alone may reveal a significant amount of information.
Furthermore, the analyst may attempt to locate potential speculative entry
points, even without the help of the trigger program. We describe ways to
address both of these next.

@@

To increase security, we instead use nested speculation to \emph{chain} entry points
together. Rather than derive
the key from a single entry point, we have each potential entry point perform
another indirect jump that the CPU cannot immediately resolve, forcing it to
speculate while already executing speculatively. The predicted target of that jump
will also be determined by the trigger program. For example, if the trigger
program makes 30 training jumps, followed by 10 additional indirect jumps, and
the payload program performs the same 30 training jumps before a stall, the CPU
will predict the payload program will also perform the next 10 jumps. If each
jump has the potential to land in up to 1024 possible locations, this would
provide in total $1024^{10} = 2^{100}$ possible keys, or 100~bits of security.
We describe our implementation of nested speculative execution in
%Section~\ref{subsec:nested-spec}.
Section~\ref{subsec:impl-aes}, where we achieve 128~bits of security. We note
that the security gained here is not a result of a single entry point
remaining secret but rather multiple independent jumps by the (unknown) trigger
program providing numerous landing points for each jump.

\FigNestedSpec
